A Kleisli-like construction for Parametric Monads, with Examples

### 2018-11-08 effects/effects.tex
Added abstract.

\begin{abstract}
\keywords{denotational semantics, category theory, game semantics}
\end{abstract}

>>>>

\begin{abstract}
  A well-known principle in denotational semantics is that adding an effect to a categorical model should correspond to the Kleisli category construction for some suitable monad.  
  Our point of departure is the observation that much recent work in semantics, particularly in game semantics, has broken away from this principle by modelling effects using categories that are not Kleisli categories.  
  Such models are usually obtained throuhg a combination of analysis and intuition and therefore, while acknowledging that this program has been very successful, we have set out to provide the beginnings of a theory which could encompass models of effects in a setting like game semantics that is not amenable to the traditional monadic approach.

  An important part of our approach will be to study parametric monads, otherwise known as lax actions, which have been studied recently by \Mellies, Katsumata and others.  
  We introduce a construction on parametric monads which generalizes the Kleisli construction and also shares one of its most striking features; namely, that it does not change the objects of the category, only the morphisms.
  We illustrate the importance of this construction by showing that a particular special case gives us a fully abstract game semantics for Probabilistic Algol.
\keywords{denotational semantics, category theory, game semantics}
\end{abstract}
